---
title: "Div II Project"
author: "Put your name here"
date: "November 20, 2019"
output: 
  html_document:
    toc: yes
    toc_float: yes
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Metadata

### Purpose

> What is the purpose of your function? What problem does it solve? When would you use it? 

### Dependencies/Setup

> Load any packages or other pre-processing steps that are necessary to make your function work in the chunk below. The chunk should be as [parsimonious](https://en.wiktionary.org/wiki/parsimonious) as possible.

```{r load, message=FALSE}
library(tidyverse)
```


### Arguments

> List the arguments your function takes. Specify the data type, default value (if applicable), and any other assumptions you are making about the value of each argument. 

- `x`: a numeric vector

### Result

> What does your function return? Specify the data type and any other assumptions you are making. 

- a numeric vector of the squared values of the input vector `x`. 

## Code

> Paste your code in the chunk below. 
>
> **Alternatively**, if your code is already in a package, you may also show the code from source using the double- colon operator and omitting the parentheses (e.g., `base::mean`). This will only work if the package is installed, so be sure to lists the correct dependencies above. 

```{r code}
square <- function(x) {
  x^2
}
```

## Examples

> Give 2-3 examples of typical usage of your function. Describe in words what is being illustrated.

This shows the first 10 perfect squares. 

```{r ex1}
square(1:10)
```

## Testing

> Provide a few examples of outputs that you expect your function will match, given a specific input. [Best if you use the [`testthat` package](https://github.com/r-lib/testthat).] 

```{r tests, message=FALSE}
square(0) == 0^2
square(10) == 10^2
square(-1) == square(1)

# using testthat
library(testthat)
expect_equal(square(0), 0^2)
expect_equal(square(10), 10^2)
expect_equal(square(-1), square(1))
```

